Using structural and evolutionary information to detect and correct pyrosequencing errors in non-coding RNAs

### 2013-05-28 JCB/results_JCB.tex
res

{\centering \url{http://csb.cs.mcgill.ca/RNApyro}\\}
The time benchmarks were performed on a MacMini 2010, 2.3GHz dual-core Intel Core i5, 8GB of RAM.
%on AMD Opteron(tm) Processor 6278  at 2.4 GHz with cache of 512 KB.20 cores and 175 GB ram.
Since typical use-cases of \RNApyro require efficiency and scalability, we present in TableFigure~\ref{fig:time}
typical runtimes required to compute the probabilities for  every nucleotide at every positions for a vast set of parameters.
For those tests, both the multiple sequence alignment and the reference sequence were generated uniformly at random,
based on a realistic random secondary structure, generated as described in Levin~\emph{et al}~\cite{Levin:2012kx}.
\TODOVlad{Add more extensive time benchmark, as a plot}
\TODOVlad{Is time benchmark still on Mac mini or mcbbigram?}

@@

\subsection{Error Correction in 16s rRNAs}
\label{sec:16S}

@@

\subsection{Error Correction in 16s rRNAs}

\TODOTous{Describe and present results????}

>>>>

{\centering \url{http://csb.cs.mcgill.ca/RNApyro}\\}
The time benchmarks were performed on an AMD Opteron(tm) Processor 6278  at 2.4 GHz with cache of 512 KB.20 cores and 175 GB ram.
Since typical use-cases of \RNApyro require efficiency and scalability, we present in TableFigure~\ref{fig:time}
typical runtimes required to compute the probabilities for  every nucleotide at every positions for a vast set of parameters.
For those tests, both the multiple sequence alignment and the reference sequence were generated uniformly at random,
based on a realistic random secondary structure, generated as described in Levin~\emph{et al}~\cite{Levin:2012kx}.
\TODOVlad{Add more extensive time benchmark, as a plot}
%\TODOVlad{Is time benchmark still on Mac mini or mcbbigram?}

@@

\subsection{Error Correction in 16s rRNAs}
\label{sec:16S}
\TODOTous{Describe and present results????}

@@
